---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

---
title: "tabexp"
output: github_document
---

# tabexp

`tabexp` is an R package for fertility estimation using exact exposure methods. The goal of `tabexp` is to create a table of births and exposure from a DHS-like birth history. It uses the same structure as the individual recode data file in DHS. You can use a data frame or a data table in R, or directly call a DHS Stata file from R.


The package was developed to reproduce and extend the logic of Stata's `tabexp.ado` and related fertility estimation procedures.

## Installation

Install the development version from GitHub:

```r
# install.packages("remotes")
remotes::install_github("schoumaker/tabexp")
```

## Main features

- Exact exposure calculations
- Age-specific fertility rates (ASFR)
- Total fertility rates (TFR)
- Replication of Stata `tabexp` procedures

## Example

Load the package:

```r
library(tabexp)
```

Example fertility calculation:

```r
# hypothetical example
result <- tabexp(
  data = births_data,
  age = "age",
  birth = "birth"
)

result
```

## Comparison with Stata

The package aims to closely reproduce the behavior of:

```stata
tabexp
```

while providing a fully R-based workflow.

## Author

Bruno Schoumaker

## License


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tabexp)
tabexp(data = AMIR54FL)
```

